Parametric controls on vegetation responses to biogeochemical forcing in the CLM5

### 2019-07-02 main_revision.tex
Updates from Overleaf

Changing \emph{leafcn} over one standard deviation from the mean TRY values, had substantial impacts on all the output variables at all sites. Higher \emph{leafcn} values decrease $N_{leaf}$, decreasing photosynthetic capacity and GPP.  In particular, at MET and HVF the higher \emph{leafcn} values had $N_{leaf}$ and photosynthetic capacities so low that GPP was almost zero Figures \ref{HVF state}, \ref{MET state}).  GPP continues to increase almost linearly with declining \emph{leafcn} (increasing $N_{leaf}$), indicating a lack of saturation of photosynthesis with respect to photosynthetic capacity.  This is consistent with the analysis by \cite{lawrence2018} who find that V${_c,max}$ numbers in CLM5 might be low compared to observations.  For NPP, respiration costs of modified $N_{leaf}$ and altered PNU (Figure \ref{btran state}) buffered the larger changes in GPP. At CAX, for example, the lowest \emph{leafcn} had a GPP 225 gC/m^{2}/y higher, while the corresponding NPP increase was only 52 gC/m^{2}/y.

@@

\emph{cn\_flex\_c} affects the degree to which plants attempt to maintain tissue C:N values near to their target when environmental costs are varying. For the state impacts here, the role of this parameter was limited, but for the step-change fertilization it was much more important, so we will discuss it's role further in the section below.

>>>>

Changing \emph{leafcn} over one standard deviation from the mean TRY values, had substantial impacts on all the output variables at all sites. Higher \emph{leafcn} values decrease $N_{leaf}$, decreasing photosynthetic capacity and GPP.  In particular, at MET and HVF the higher \emph{leafcn} values had $N_{leaf}$ and photosynthetic capacities so low that GPP was almost zero Figures \ref{HVF state}, \ref{MET state}).  GPP continues to increase almost linearly with declining \emph{leafcn} (increasing $N_{leaf}$), indicating a lack of saturation of photosynthesis with respect to photosynthetic capacity.  This is consistent with the analysis by \cite{lawrence2018} who find that V${_c,max}$ numbers in CLM5 might be low compared to observations.  For NPP, respiration costs of modified $N_{leaf}$ and altered PNU (Figure \ref{btran state}) buffered the larger changes in GPP. At CAX, for example, the lowest \emph{leafcn} had a GPP 225 gC/m$^{2}$/y higher, while the corresponding NPP increase was only 52 gC/$m^{2}$/y.

@@

\emph{cn\_flex\_c} affects the degree to which plants attempt to maintain tissue C:N values near to their target when environmental costs are varying. For the pre-fertilization state impacts here, the role of this parameter was limited, but for the step-change fertilization it was much more important, so we discuss its role further in the section below.
